### 2012-05-26 doc/hmcsa_adjoint_vs_direct/direct_vs_adjoint.tex
fixed a few typos in the hmcsa tex note

\audience{\email{Stuart Slattery}{uy7@ornl.gov},
          \email{Thomas Evans}{tme@ornl.gov},
          \email{Greg Davidson}{gqe@ornl.gov}}

@@

Using this form, we can approximate the terms in the series with a
random walk sequence as outlined in \cite{hammersley_1964}. There are
two primary ways of achieving this; through a direct sequence and an
adjoint sequence. For the direct sequence, analagous (and
inconveniently so) to an adjoint stochastic transport calculation,
each term in the source is simulated with an equivalent number of
random walk histories. Each step in the random walk sequence will
contribute to the solution in the starting source state. For the
adjoint sequence, analagous to a forward stochastic transport
calculation, the source term is sampled with a set number of random
walk histories, meaning that regions of larger source will be sampled
as a starting state more regularly. In this case, each step in the
random walk sequence will contribute to the state in which it
currently resides, not the current source state. It is this set of
primary differences between the two solution methods that will dictate
solver performance with MCSA.

>>>>

\audience{\email{Stuart Slattery}{uy7@ornl.gov},
          \email{Thomas Evans}{tme@ornl.gov},
          \email{Greg Davidson}{gqe@ornl.gov},
          \email{Scott Mosher}{moshersw@ornl.gov}}

@@

Using this form, we can approximate the terms in the series with a
random walk sequence as outlined in \cite{hammersley_1964}. There are
two primary ways of achieving this; through a direct sequence and an
adjoint sequence. For the direct sequence, analagous (and
inconveniently so) to an adjoint stochastic transport calculation,
each term in the source is simulated with an equivalent number of
random walk histories. Each step in the random walk sequence will
contribute to the solution in the starting source state. For the
adjoint sequence, analagous to a forward stochastic transport
calculation, the source term is sampled with a set number of random
walk histories, meaning that regions of larger source will be sampled
as a starting state more regularly. In this case, each step in the
random walk sequence will contribute to the state in which it
currently resides, not the starting source state. It is this set of
primary differences between the two solution methods that will dictate
stochastic solver performance with MCSA.
